### 2019-07-30 7_conclusion.tex
Update conclusion to match intro.

\item While some systems support task granularities as small as a few
  microseconds, this applies only to small CPU-based clusters. Adding
  accelerators or moving to clusters of hundreds of nodes raises the
  METG that any system can achieve by over an order of magnitude.

\item Systems that support asynchronous execution show benefits under
  load imbalanced workloads, or workloads with balanced computation
  and communication. However, these gains can be nullified by
  high baseline overheads.

\item Systems for large scale data analysis require very large tasks
  (in the tens of seconds) to scale beyond small numbers of nodes,
  reflecting the very coarse tasks and lack of need for strong scaling
  performance in current workloads.

\item The newer task-based systems have performance sufficient for
  weak scaling many HPC workloads, but more work is needed to strong
  scale the most demanding applications.

>>>>

\item While some systems support task granularities as small as 390~ns, this applies only to trivial dependencies and small CPU-based clusters. A number of factors (non-trivial dependencies, accelerators and cluster sizes in the hundreds of nodes) raise the
  METG that any system can reliably achieve by over an order of magnitude: 100~\textmu{}s is a reasonable bound for most applications running at scale with current technologies.

\item Systems that support asynchronous execution show benefits under
  balanced computation
  and communication, and load imbalance. However, these gains can be nullified by
  high baseline overheads.

\item Systems for large scale data analysis require very large tasks
  (tens of seconds) to scale beyond small node counts,
  reflecting the very coarse tasks and lack of need for strong scaling
  performance in current workloads.

\item Newer task-based systems have performance sufficient for
  weak scaling many HPC workloads, but more work is needed to strong
  scale the most demanding codes.
